% ════════════════════════════════════════════════════════════════════════════
%  APPENDIX A --- TAHKIK INFERENCE SERVER
%  Short summary of the production stack in ~/tahkik-server.
% ════════════════════════════════════════════════════════════════════════════
\chapter{Tahkik Inference Server}
\label{app:server}

The Tahkik backend is a three-container Docker Compose stack deployed on a
single DigitalOcean droplet (provisioned by \texttt{scripts/provision-droplet.sh}):
\textbf{Caddy} terminates TLS and routes traffic, a \textbf{Go} API
gateway on port \texttt{8080} handles REST traffic, and a \textbf{Python
FastAPI} service on port \texttt{7860} hosts three AI models and exposes
the streaming endpoint. The Flutter client talks to the public hostname
and consumes three endpoints: \texttt{POST /api/v1/evaluate} (batch
audio upload), \texttt{WS /ws/stream} (real-time partial transcription),
and \texttt{GET /api/v1/system-health} (host metrics and inference
latency).

\begin{figure}[H]
\centering
\begin{tikzpicture}[
  component/.style={
    draw=teal!60!black, rounded corners=8pt, minimum width=3.2cm,
    minimum height=1.6cm, fill=tealbg, font=\small\bfseries,
    text=teal!80!black, align=center
  },
  arrow/.style={-latex, thick, teal!60!black},
  label/.style={font=\scriptsize, color=slategray}
]
\node[component] (client)  at (0,    0)  {Flutter\\Mobile Client};
\node[component] (caddy)   at (4,    0)  {Caddy\\(:80 / :443)};
\node[component] (go)      at (8,    1.2){Go API\\(:8080)};
\node[component] (py)      at (8,   -1.2){Python FastAPI\\(:7860)};
\node[component] (models)  at (12,  -1.2){3 AI models\\(see below)};

\draw[arrow] (client) -- node[label, above] {HTTPS / WSS} (caddy);
\draw[arrow] (caddy)  -- node[label, above] {/api/v1/* /health} (go);
\draw[arrow] (caddy)  -- node[label, below] {/ws/*} (py);
\draw[arrow] (go)     -- node[label, right] {/evaluate} (py);
\draw[arrow] (py)     -- node[label, above] {inference} (models);
\end{tikzpicture}
\caption{Production stack: Caddy reverse proxy, Go API gateway, and Python
FastAPI service hosting the three inference models.}
\label{fig:app_server_arch}
\end{figure}

\section{The three models}
\label{sec:app_server_models}

The Python service loads three complementary models. Each one is
responsible for a distinct slice of the recitation analysis; the
combined output is merged into a single JSON response.

\begin{itemize}
  \item \textbf{\texttt{benhadjermed/tahkik-small-warsh}} --- our
        Whisper-Small Warsh fine-tune (Appendix~\ref{app:training}).
        \emph{Role:} detects \textbf{wrong words} and wrong
        \textbf{tashkeel} (diacritics) in the reciter's transcription
        against the expected ayah text.
  \item \textbf{\texttt{nvidia/stt\_ar\_fastconformer\_hybrid\_large\_pcd\_v1.0}}
        --- NVIDIA NeMo FastConformer Hybrid CTC/RNNT for Arabic.
        \emph{Role:} the RNNT head provides high-accuracy transcription
        and word/character timestamps; the CTC head is reused for forced
        alignment against the reference text so each letter receives a
        real start/end time.
  \item \textbf{\texttt{obadx/muaalem-model-v3\_2}} --- multi-level CTC
        phonetic model. \emph{Role:} per-letter Tajweed grading. Its
        per-frame predictions feed the rules engine
        (\texttt{python/hf\_space/rules/}) which checks madd duration,
        intrinsic sifat, qalqala, ghunna, and tafkheem.
\end{itemize}

\section{Ahkam (Tajweed rules) graded}
\label{sec:app_server_ahkam}

Table~\ref{tab:app_ahkam} lists every family of rules that the rules
engine currently checks. The corresponding source modules live under
\texttt{tahkik-server/python/hf\_space/rules/}.

\begin{longtable}{p{2.6cm} p{4.2cm} p{7.4cm}}
\caption{Ahkam graded by the rules engine in \texttt{python/hf\_space/rules/}.}
\label{tab:app_ahkam} \\
\toprule
\textbf{Family} & \textbf{Sub-rule} & \textbf{What is checked} \\
\midrule
\endfirsthead
\multicolumn{3}{c}{\textit{(continued)}} \\
\toprule
\textbf{Family} & \textbf{Sub-rule} & \textbf{What is checked} \\
\midrule
\endhead

\multirow{8}{*}{\textbf{Madd}}
  & \texttt{tabii}            & Natural madd, 2 counts (window 1.5--2.7). \\
  & \texttt{badal}            & Hamza precedes madd letter, qasr 2 counts. \\
  & \texttt{muttasil}         & Madd + hamza in the same word, 6 counts (window 5.0--7.5). \\
  & \texttt{munfasil}         & Madd at word end + hamza on the next word, 6 counts. \\
  & \texttt{lazim\_muthaqqal} & Madd followed by a shaddah, 6 counts. \\
  & \texttt{lazim\_mukhaffaf} & Madd followed by a permanent sukun, 6 counts. \\
  & \texttt{aarid}            & Word-final madd at waqf, qasr 2 counts. \\
  & \texttt{lin}              & Lin letter (waw/ya sakin after fatha) at waqf, 2 counts. \\
\midrule
\multirow{3}{*}{\textbf{Ghunna}}
  & Ikhfa                     & Nun sakin / tanwin followed by an ikhfa letter --- partial nasalisation held $\sim$2 counts. \\
  & Idgham (with ghunna)      & Nun sakin / tanwin merged into the next letter with full nasalisation. \\
  & Iqlab                     & Nun sakin / tanwin followed by \emph{ba} converts to a \emph{mim}-coloured ghunna. \\
\midrule
\multirow{2}{*}{\textbf{Qalqala}}
  & Sughra (minor)            & Sukun on a qalqala letter (\emph{qaf, taa, baa, jim, dal}) inside a word --- light echo. \\
  & Kubra (major)             & Qalqala letter at waqf --- stronger, more pronounced echo. \\
\midrule
\multirow{3}{*}{\textbf{Tafkheem}}
  & Isti'l\=a letters         & The seven heavy letters (\emph{kha, sad, dad, ghain, taa, qaf, dha}) always pronounced thick. \\
  & Conditional \emph{ra}     & Tafkheem / tarqiq on \emph{ra} decided by surrounding haraka and sukun. \\
  & Laf\.z al-Jal\=ala        & Heavy \emph{lam} of \emph{All\=ah} after fatha/damma, light after kasra. \\
\midrule
\multirow{7}{*}{\textbf{Intrinsic sifat}}
  & Hams / Jahr               & Voiceless vs.\ voiced articulation per letter. \\
  & Shidda / Rakhawa          & Stop vs.\ continuant. \\
  & Safeer                    & Whistled articulation on \emph{sad, zay, sin}. \\
  & Tafashie                  & Air spread on \emph{shin}. \\
  & Istitala                  & Tongue extension on \emph{dad}. \\
  & Itbaq                     & Mouth closure on \emph{sad, dad, taa, dha}. \\
  & Tikraar                   & Trill control on \emph{ra}. \\
\bottomrule
\end{longtable}

\section{Request flow}
\label{sec:app_server_flow}

A client uploads an audio clip and (optionally) the ayah text it
expected the reciter to say. The Go gateway streams the file to the
Python service, which runs FastConformer for transcription and
CTC-aligned timestamps, then asks the muaalem grader for per-letter
phoneme predictions. The rules engine walks the reference text,
generates one expected letter per base character, compares it against
the muaalem output, and emits a \texttt{TajweedError} for each
mismatch. The response contains the transcription, a confidence score,
the list of errors with millisecond ranges, and the calibrated
\texttt{haraka\_ms} used for grading. Waqf positions are derived from
acoustic silence (${\geq}\,300$\,ms) rather than from ayah boundaries,
so \texttt{aarid} and \texttt{lin} are graded only where the reciter
actually paused.
