\chapter*{Bibliography}
\addcontentsline{toc}{chapter}{Bibliography}

\begin{enumerate}
  \item OpenAI, ``Whisper: Robust Speech Recognition via Large-Scale Weak Supervision,'' 2022. Available: \url{https://openai.com/research/whisper}

  \item Google, ``Flutter --- Build apps for any screen,'' 2024. Available: \url{https://flutter.dev}

  \item Meta, ``React --- A JavaScript library for building user interfaces,'' 2024. Available: \url{https://react.dev}

  \item Supabase, ``Supabase --- The open source Firebase alternative,'' 2024. Available: \url{https://supabase.com}

  \item Riverpod, ``Riverpod --- A reactive caching and data-binding framework,'' 2024. Available: \url{https://riverpod.dev}

  \item PyTorch, ``PyTorch --- An open source machine learning framework,'' 2024. Available: \url{https://pytorch.org}

  \item Microsoft, ``Visual Studio Code --- Code Editing. Redefined,'' 2024. Available: \url{https://code.visualstudio.com}

  \item Git, ``Git --- Distributed Version Control System,'' 2024. Available: \url{https://git-scm.com}

  \item GitHub, ``GitHub --- Where the world builds software,'' 2024. Available: \url{https://github.com}

  \item Vite, ``Vite --- Next Generation Frontend Tooling,'' 2024. Available: \url{https://vitejs.dev}

  \item TanStack, ``TanStack Query --- Powerful asynchronous state management,'' 2024. Available: \url{https://tanstack.com/query}

  \item A. Radford et al., ``Robust Speech Recognition via Large-Scale Weak Supervision,'' in \textit{Proceedings of the International Conference on Machine Learning (ICML)}, 2023.

  \item S. Al-Fedaghi, ``Unified Modeling Language (UML) Sequence Diagrams: A Systematic Review,'' \textit{International Journal of Software Engineering}, vol. 12, no. 3, pp. 45--62, 2021.

  \item K. Schwaber and J. Sutherland, ``The Scrum Guide,'' Scrum.org, 2020.
\end{enumerate}
