% ════════════════════════════════════════════════════════════════════════════
%  GENERAL CONCLUSION (Combined Edition)
% ════════════════════════════════════════════════════════════════════════════
\chapter*{General Conclusion}
\addcontentsline{toc}{chapter}{General Conclusion}
\label{ch:general_conclusion}

The primary objective of this Final Year Project was to design, develop,
and deploy a comprehensive digital platform dedicated to the learning and
perfection of Quranic recitation and Tajweed rules. Through the
development of \textbf{Tahkik}, we have demonstrated how modern technology
--- specifically Artificial Intelligence, cross-platform mobile
development, and cloud-based backend services --- can be leveraged to
address the traditional challenges of accessibility and personalised
feedback in Islamic education.

\section*{Synthesis}

The body of this report (Chapters~\ref{ch:state_of_art} to
\ref{ch:implementation}) surveys the existing Quranic e-learning
landscape, models the platform with UML, and documents the
implementation of the Flutter mobile application and the React
administrator/teacher dashboard, both backed by Supabase. The two
supporting workstreams --- the production inference server (Caddy + Go
+ Python FastAPI hosting three AI models) and the Whisper-Small
fine-tuning that produced the \texttt{tahkik-small-warsh} checkpoint
--- are summarised in Appendix~\ref{app:server} and
Appendix~\ref{app:training} respectively, where the reader will find
the system diagram, the three-model breakdown, the Tajweed rules
graded today, and the training configuration used in
\texttt{project-L3/}.

\begin{emeraldbox}[title=Key Contributions of the Tahkik Project]
\begin{enumerate}
  \item A cross-platform mobile application (Flutter) providing an
        intuitive Quran reading and recitation recording experience with
        the official KFGQPC Warsh font.
  \item A real-time AI-driven recitation evaluation pipeline combining
        three complementary models --- our fine-tuned Whisper-Small for
        wrong-word and tashkeel detection, an NVIDIA NeMo
        FastConformer for transcription and CTC alignment, and the
        Muaalem model for per-letter Tajweed grading --- with
        WebSocket streaming for sub-second partial transcriptions.
  \item A dedicated React/TypeScript dashboard empowering teachers to
        review, correct, and certify (\textit{Ijaza}) student
        recitations, with a complementary administrator workspace for
        platform analytics and live AI/system telemetry.
  \item A production-grade containerised inference server combining
        Caddy, Go, and a Python FastAPI service that co-hosts the three
        model checkpoints (fine-tuned Whisper-Small, NeMo
        FastConformer, and Muaalem) and merges their outputs into a
        single feedback response, deployable on a single DigitalOcean
        droplet via a one-shot provisioning script.
  \item A Madd Tajweed analyser implementing eight Warsh/Azraq rules
        with auto-calibrated haraka length and CTC-derived per-letter
        timings.
  \item A reproducible Warsh dataset preparation pipeline and two
        fine-tuned Whisper checkpoints (\texttt{tahkik-basic-warsh},
        \texttt{tahkik-small-warsh}).
  \item A documented Word Error Rate reduction from $34.62\%$ to
        $\mathbf{6.00\%}$ through multi-reciter training and Warsh-aware
        text normalisation.
  \item A human-in-the-loop architecture combining AI efficiency with
        irreplaceable teacher expertise.
\end{enumerate}
\end{emeraldbox}

\section*{Limitations}

Despite these achievements, certain limitations remain:
\begin{itemize}
  \item The AI model's accuracy varies across reciters outside the
        training set and across regional accents.
  \item The current implementation requires an internet connection for
        AI processing (no on-device inference yet).
  \item The gamification and social-interaction features are
        intentionally limited in this first release.
  \item The Madd analyser locks to the canonical \emph{qasr} (2-count)
        wajh; multi-wajh grading is left as future work.
  \item The dataset is concentrated on three male reciters; coverage of
        female and child voices remains a gap.
\end{itemize}

\begin{goldbox}[title=Future Perspectives]
\begin{itemize}
  \item Continue fine-tuning the recognition engine on additional Warsh
        reciters (women, children, regional accents) and progressively
        on other riwayat (Hafs, Qaloon, ad-Duri).
  \item Add offline AI inference using on-device, quantised model
        variants for low-bandwidth environments.
  \item Extend the Tajweed analyser beyond madd: idgham, ikhfa,
        qalqala, ghunnah, and tafkhim/tarqiq detection.
  \item Implement gamification features (badges, leaderboards, learning
        paths) to increase learner engagement.
  \item Integrate live tutoring sessions with built-in audio/video
        between teachers and students, complementing the existing chat
        and certification flows.
  \item Move to a multi-region deployment with horizontal scaling,
        Prometheus/Grafana observability, and automated blue/green
        deployments via GitHub Actions.
\end{itemize}
\end{goldbox}

\begin{emeraldbox}[title=Closing Statement]
\begin{center}
\large\itshape
``Read! In the name of your Lord who created.''\\[6pt]
\normalsize\normalfont\color{black} --- Surah Al-Alaq, Verse 1
\end{center}
\vspace{6pt}
\normalsize
The Tahkik platform represents a meaningful step forward in digital
Islamic education. By harmonising the efficiency of AI with the
irreplaceable expertise of human teachers, Tahkik aspires to make
high-quality Tajweed instruction accessible to a global audience,
preserving the oral tradition of the Quran for generations to come.
\end{emeraldbox}
