% ════════════════════════════════════════════════════════════════════════════
%  COMBINED BIBLIOGRAPHY
%  Merges entries from the three source reports:
%    * tahkik_pfe/back/bibliography.tex          (web/tooling references)
%    * server_report_part4.tex (References)      (NeMo + server stack)
%    * model train.tex (Bibliography)            (Whisper + ML stack)
%
%  Uses the \begin{thebibliography} environment so the \cite{key} calls from
%  the model train.tex body still resolve.
% ════════════════════════════════════════════════════════════════════════════
\chapter*{Bibliography}
\addcontentsline{toc}{chapter}{Bibliography}

\begin{thebibliography}{99}

% ─── ML / SPEECH RECOGNITION (Whisper, Transformers, NeMo) ──────────────────
\bibitem{radford2022whisper}
A.~Radford, J.~W.~Kim, T.~Xu, G.~Brockman, C.~McLeavey, and I.~Sutskever,
``Robust Speech Recognition via Large-Scale Weak Supervision,''
in \textit{Proceedings of the 40th International Conference on Machine
Learning (ICML)}, 2023.

\bibitem{vaswani2017attention}
A.~Vaswani, N.~Shazeer, N.~Parmar, J.~Uszkoreit, L.~Jones, A.~N.~Gomez,
{\L}.~Kaiser, and I.~Polosukhin,
``Attention Is All You Need,''
in \textit{Advances in Neural Information Processing Systems (NeurIPS)},
2017.

\bibitem{paszke2019pytorch}
A.~Paszke, S.~Gross, F.~Massa, A.~Lerer, J.~Bradbury, G.~Chanan,
T.~Killeen \textit{et al.},
``PyTorch: An Imperative Style, High-Performance Deep Learning Library,''
in \textit{Advances in Neural Information Processing Systems (NeurIPS)},
2019. Available: \url{https://pytorch.org}

\bibitem{wolf2020transformers}
T.~Wolf \textit{et al.},
``Transformers: State-of-the-Art Natural Language Processing,''
in \textit{Proceedings of EMNLP: System Demonstrations}, 2020.
Available: \url{https://huggingface.co/transformers}

\bibitem{lhoest2021datasets}
Q.~Lhoest \textit{et al.},
``Datasets: A Community Library for Natural Language Processing,''
in \textit{Proceedings of EMNLP: System Demonstrations}, 2021.
Available: \url{https://huggingface.co/datasets}

\bibitem{rapidfuzz}
M.~Bachmann,
``RapidFuzz: Rapid String Matching Library for Python and C++,''
2024. Available: \url{https://github.com/rapidfuzz/RapidFuzz}

\bibitem{tarteelmodel}
Tarteel AI,
``\texttt{tarteel-ai/whisper-base-ar-quran} --- Quranic Arabic Whisper
fine-tune,'' Hugging Face Hub, 2023.
Available: \url{https://huggingface.co/tarteel-ai/whisper-base-ar-quran}

\bibitem{fawazapi}
F.~Ahmed, ``Quran API,'' 2023.
Available: \url{https://github.com/fawazahmed0/quran-api}

\bibitem{everyayah}
``EveryAyah.com --- audio recitations of the Holy Quran,'' 2024.
Available: \url{https://everyayah.com/data/}

\bibitem{alqurancloud}
``Al~Quran Cloud API,'' 2024.
Available: \url{https://alquran.cloud/api}

\bibitem{huggingfacehub}
Hugging Face,
``The AI community building the future,'' 2024.
Available: \url{https://huggingface.co}

\bibitem{ctranslate2}
G.~Klein \textit{et al.},
``CTranslate2: Fast and Efficient Inference for Transformer Models,''
2023. Available: \url{https://github.com/OpenNMT/CTranslate2}

\bibitem{kingfahd}
King Fahd Glorious Quran Printing Complex,
``KFGQPC Warsh Uthmanic Script Hafs --- Quranic Arabic typeface,''
2024. Available: \url{https://qurancomplex.gov.sa}

\bibitem{tajweedoverview}
A.~Czerepinski,
\textit{Tajweed Rules of the Quran},
Dar Al-Khair, 3rd ed., 2010.

\bibitem{warshhistory}
M.~A.~A.~Sukkar,
\textit{The Warsh Reading: History, Phonology, and Orthography},
Riwaya Studies Press, 2017.

% ─── INFERENCE STACK (NeMo, FastConformer, FastAPI, Caddy, Go, Docker) ──────
\bibitem{nemo}
NVIDIA Corporation. \emph{NeMo: A Toolkit for Conversational AI}.
Available: \url{https://github.com/NVIDIA/NeMo}

\bibitem{fastconformer}
D.~Rekesh, N.~R.~Koluguri \textit{et al.}
``Fast Conformer with Linearly Scalable Attention for Efficient Speech
Recognition,'' ASRU 2023.
Available: \url{https://arxiv.org/abs/2305.05084}

\bibitem{nemoarabic}
NVIDIA. \emph{stt\_ar\_fastconformer\_hybrid\_large\_pcd\_v1.0 --- model card}.
Available: \url{https://huggingface.co/nvidia/stt_ar_fastconformer_hybrid_large_pcd_v1.0}

\bibitem{rnnt}
A.~Graves. ``Sequence Transduction with Recurrent Neural Networks,''
ICML 2012 Representation Learning Workshop.
Available: \url{https://arxiv.org/abs/1211.3711}

\bibitem{ctc}
A.~Graves, S.~Fern\'andez, F.~Gomez, J.~Schmidhuber.
``Connectionist Temporal Classification: Labelling Unsegmented Sequence
Data with Recurrent Neural Networks,'' ICML 2006.

\bibitem{torchaudio_align}
PyTorch Team. \emph{Forced Alignment with Wav2Vec2 / CTC ---
\texttt{torchaudio.functional.forced\_align}}.
Available: \url{https://pytorch.org/audio/stable/generated/torchaudio.functional.forced_align.html}

\bibitem{fastapi}
S.~Ram\'irez. \emph{FastAPI: Modern, fast (high-performance) web framework}.
Available: \url{https://fastapi.tiangolo.com}

\bibitem{uvicorn}
T.~Christie. \emph{Uvicorn --- The lightning-fast ASGI server}.
Available: \url{https://www.uvicorn.org}

\bibitem{caddy}
M.~Holt et al. \emph{Caddy --- The Ultimate Server with Automatic HTTPS}.
Available: \url{https://caddyserver.com}

\bibitem{gohttp}
The Go Authors. \emph{Package net/http}.
Available: \url{https://pkg.go.dev/net/http}

\bibitem{coderws}
Coder. \emph{github.com/coder/websocket --- minimal and idiomatic WebSocket
library for Go}.
Available: \url{https://github.com/coder/websocket}

\bibitem{docker}
Docker, Inc. \emph{Docker Engine documentation}.
Available: \url{https://docs.docker.com/engine/}

\bibitem{compose}
Docker, Inc. \emph{Docker Compose specification}.
Available: \url{https://docs.docker.com/compose/}

\bibitem{librosa}
B.~McFee. \emph{librosa: Audio and music signal analysis in Python}.
Available: \url{https://librosa.org}

\bibitem{warsh}
\emph{Tariq al-Azraq (Warsh `an Naf{\^\i}' transmission)} ---
riwaya documentation in the Tajweed literature.
Standard reference works on Madinah Mushaf and Tariq Azraq variants.

\bibitem{tahkikserver}
M.~Ben~Hadj. \emph{Tahkik Server Source Code Repository}.
Available: \url{https://github.com/mohamedbenhadjer/tahkik-server}

% ─── PLATFORM (Flutter, React, Supabase, Vite, ...) ─────────────────────────
\bibitem{flutter}
Google. \emph{Flutter --- Build apps for any screen}, 2024.
Available: \url{https://flutter.dev}

\bibitem{reactweb}
Meta. \emph{React --- A JavaScript library for building user interfaces}, 2024.
Available: \url{https://react.dev}

\bibitem{supabase}
Supabase. \emph{Supabase --- The open source Firebase alternative}, 2024.
Available: \url{https://supabase.com}

\bibitem{riverpod}
Riverpod. \emph{Riverpod --- A reactive caching and data-binding framework},
2024. Available: \url{https://riverpod.dev}

\bibitem{vscode}
Microsoft. \emph{Visual Studio Code --- Code Editing. Redefined.}, 2024.
Available: \url{https://code.visualstudio.com}

\bibitem{git}
Git. \emph{Git --- Distributed Version Control System}, 2024.
Available: \url{https://git-scm.com}

\bibitem{github}
GitHub. \emph{GitHub --- Where the world builds software}, 2024.
Available: \url{https://github.com}

\bibitem{vite}
Vite. \emph{Vite --- Next Generation Frontend Tooling}, 2024.
Available: \url{https://vitejs.dev}

\bibitem{tanstack}
TanStack. \emph{TanStack Query --- Powerful asynchronous state management},
2024. Available: \url{https://tanstack.com/query}

\bibitem{scrum}
K.~Schwaber and J.~Sutherland. \emph{The Scrum Guide}, Scrum.org, 2020.

\bibitem{umlseq}
S.~Al-Fedaghi. ``Unified Modeling Language (UML) Sequence Diagrams: A
Systematic Review,'' \textit{International Journal of Software Engineering},
vol.~12, no.~3, pp.~45--62, 2021.

\end{thebibliography}
