\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

\section*{Abstract}
Our final study project is a mobile and web platform dedicated to Quran recitation and Tajweed learning powered by Artificial Intelligence. Tahkik aims to bridge the gap between traditional Quranic education and modern technology by providing learners with instant AI-driven feedback on their recitation, while empowering teachers with a comprehensive dashboard to review and manage student progress. The mobile application, built with Flutter, allows users to read the Quran, record their recitation, and receive real-time pronunciation analysis using the Whisper AI model. The web dashboard, developed with React and TypeScript, provides teachers and administrators with tools for recitation review, student management, and platform analytics. The system uses Supabase as its backend-as-a-service for authentication, database, and real-time capabilities.

\textbf{Keywords:} Quran, Tajweed, AI, Speech Recognition, Whisper, Flutter, React, Supabase, Mobile Application, E-Learning.

\vspace{1cm}

\section*{R\'esum\'e}
Notre projet de fin d'\'etudes est une plateforme mobile et web d\'edi\'ee \`a l'apprentissage de la r\'ecitation du Coran et du Tajweed, aliment\'ee par l'Intelligence Artificielle. Tahkik vise \`a combler le foss\'e entre l'\'education coranique traditionnelle et la technologie moderne en fournissant aux apprenants un retour instantan\'e g\'en\'er\'e par l'IA sur leur r\'ecitation, tout en offrant aux enseignants un tableau de bord complet pour examiner et g\'erer les progr\`es des \'etudiants. L'application mobile, d\'evelopp\'ee avec Flutter, permet aux utilisateurs de lire le Coran, d'enregistrer leur r\'ecitation et de recevoir une analyse de prononciation en temps r\'eel. Le tableau de bord web, d\'evelopp\'e avec React et TypeScript, fournit aux enseignants et administrateurs des outils de gestion.

\textbf{Mots-cl\'es:} Coran, Tajweed, IA, Reconnaissance Vocale, Whisper, Flutter, React, Supabase, Application Mobile, E-Learning.


\newpage
