\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

\section*{Abstract}
Our final study project, \textbf{Tahkik}, is a mobile and web platform
dedicated to Quran recitation and Tajweed learning, powered by Artificial
Intelligence. The platform aims to bridge the gap between traditional
Quranic education and modern technology by providing learners with instant
AI-driven feedback on their recitation, while empowering teachers with a
comprehensive dashboard to review and manage student progress.

The mobile application, built with Flutter, allows users to read the Quran
in the Warsh script, record their recitation, and receive real-time
pronunciation analysis. The web dashboard, developed with React and
TypeScript on top of Supabase, provides teachers and administrators with
tools for recitation review, student management, certificate (Ijaza)
issuance, subscription management, and live AI/system telemetry.

Behind the application, a containerised inference stack --- a Caddy
reverse proxy, a Go API gateway, and a Python FastAPI server hosting an
NVIDIA NeMo \textit{FastConformer Hybrid CTC/RNNT} model --- delivers
batch and streaming Arabic speech recognition. A Tajweed (madd) analyser
running on top of the CTC head grades the recitation against the
Warsh~`an~Naf{\^\i}' canonical text. To specialise the recognition engine
on the Warsh riwaya, we built a 13{,}024-verse three-reciter dataset
and fine-tuned a Whisper checkpoint, reducing the Word Error Rate from
$48.4\%$ to $25.5\%$ on a held-out Warsh test split.

This combined report consolidates: (1)~the main dissertation that
describes the platform's mobile and web layers, (2)~the technical report
that documents the inference server architecture, API contracts, and
deployment, and (3)~the companion AI/ML report that describes the dataset
preparation pipeline, the quality-assurance loop, the fine-tuning runs,
and the WER analysis.

\textbf{Keywords:} Quran, Tajweed, Warsh, AI, Speech Recognition, Whisper,
NeMo FastConformer, Flutter, React, Go, FastAPI, Supabase, Mobile
Application, E-Learning, WebSocket Streaming, Fine-Tuning.

\vspace{0.8cm}

\section*{R\'esum\'e}
Notre projet de fin d'\'etudes, \textbf{Tahkik}, est une plateforme
mobile et web d\'edi\'ee \`a l'apprentissage de la r\'ecitation du Coran
et du Tajweed, aliment\'ee par l'Intelligence Artificielle. La plateforme
vise \`a combler le foss\'e entre l'\'education coranique traditionnelle
et la technologie moderne en fournissant aux apprenants un retour
instantan\'e g\'en\'er\'e par l'IA sur leur r\'ecitation, tout en offrant
aux enseignants un tableau de bord complet pour examiner et g\'erer les
progr\`es des \'etudiants.

L'application mobile, d\'evelopp\'ee avec Flutter, permet aux utilisateurs
de lire le Coran en \'ecriture Warsh, d'enregistrer leur r\'ecitation et
de recevoir une analyse de prononciation en temps r\'eel. Le tableau de
bord web, d\'evelopp\'e avec React et TypeScript par-dessus Supabase,
fournit aux enseignants et aux administrateurs des outils de gestion.

Derri\`ere l'application, une pile d'inf\'erence containeris\'ee
(Caddy + serveur Go + serveur Python FastAPI h\'ebergeant un mod\`ele
NVIDIA NeMo \textit{FastConformer Hybride CTC/RNNT}) assure la
reconnaissance vocale arabe en mode batch et en streaming. Un analyseur
de Tajweed (madd) bas\'e sur l'alignement forc\'e CTC \'evalue la
r\'ecitation par rapport au texte canonique de Warsh~`an~Naf{\^\i}'.
Pour sp\'ecialiser le moteur de reconnaissance sur la riwaya Warsh, nous
avons construit un jeu de donn\'ees de 13{\,}024 versets et trois
r\'ecitateurs et affin\'e un mod\`ele Whisper, r\'eduisant le taux
d'erreur de mots (WER) de $48{,}4\%$ \`a $25{,}5\%$.

Ce rapport combin\'e regroupe: (1)~le m\'emoire principal d\'ecrivant
les couches mobile et web, (2)~le rapport technique du serveur
d'inf\'erence, et (3)~le rapport compl\'ementaire d'IA d\'ecrivant la
pr\'eparation des donn\'ees, l'assurance qualit\'e, les entra{\^\i}nements
et l'analyse des r\'esultats.

\textbf{Mots-cl\'es:} Coran, Tajweed, Warsh, IA, Reconnaissance Vocale,
Whisper, NeMo FastConformer, Flutter, React, Go, FastAPI, Supabase,
Application Mobile, E-Learning, Streaming WebSocket, Affinage.

\newpage
